\item \begin{theorem}{()} \quad\quad
    \begin{itemize}
        \item (\textbf{FALSE}) For two functions $f(n)$ and $g(n)$, either $f(n) = O(g(n))$ or $f(n) = \Omega((f(n))$.
        Counterexample:\begin{equation}
            \begin{aligned}
                f(n) & = \begin{cases}
                    1, \ \text{if} \ n = 2k \\
                    0, \ \text{if} \ n = 2k + 1
                \end{cases} \\
                g(n) & = \begin{cases}
                    0, \ \text{if} \ n = 2k \\
                    1, \ \text{if} \ n = 2k + 1
                \end{cases} 
            \end{aligned}
        \end{equation}
        \item For any uniform cost RAM program $T(n) = \Omega(S(n))$, where $S(n)$ is the space an algorithm uses for an input of size $n$.
        \item The capacity of each edge of a flow network can be floating-point, and it can be solved by linear programming.
        \item A flow network of multiple sources can be reduced to a single source.
        \item (\textbf{FALSE}) The value of any flow of a flow network is bounded by the capacity of only at most $O(n)$ cuts.
        \item 2-coloring: $O(n^2)$, 3-coloring, 4-coloring: superpolynomial.
        \item Weighted-union heuristic: Append the \textbf{smaller} list onto the \textbf{longer} list, with ties broken arbitrarily.
        \item $n! \neq \Theta(n^n)$.
        \item A DAG with $n$ vertices can \textbf{NOT} have more than $\binom{n}{2}$ edges.
        \item Longest palindrome subsequence: \begin{equation}
            \begin{aligned}
                & L(i, j) = \begin{cases}
                    0 &, i = j + 1 \\
                    1 &, i = j \\
                    L(i + 1, j - 1) + 2 &, i < j \land s[i] = s[j] \\
                    \max(L(i + 1, j), L(j, j - 1)) &, \text{otherwise}
                \end{cases} \\
                & \text{where} \ L[1 \cdots n][1 \cdots n], s[1 \cdots n]
            \end{aligned}
        \end{equation}
        \item Minimum triangulation: \begin{equation}
            c(i, j) = \begin{cases}
                0 &, j < i + 2 \\
                \min_{i < k < j}\{c(i, k) + c(k, j) + dist(i, j) + dis(j, k) + dist(k, j)\} &, \text{otherwise}
            \end{cases}
        \end{equation} \begin{lstlisting}[caption={Minimum triangulation.}, captionpos=b]
            double triangulation(Point P[], int n) {
                if (n < 3)
                    return 0;
                
                double c[n][n];
                for (int gap = 0, gap < n; gap++) {
                    for(int i = 0, j = gap; j < n; i++, j++) {
                        if (j < i + 2)
                            c[i][j] = 0.0;
                        else {
                            c[i][j] = MAX;
                            for (int k = i + 1; k < j; k++) {
                                double val = c[i][k] + c[k][j] + wt(P, i, j, k);
                                if (c[i][j] > val)
                                    c[i][j] = val;
                            }
                        }
                    }
                }

                return c[0][n - 1];
            }
        \end{lstlisting}
        \item Sort $n$ integers ranged from $0$ to $n^2 - 1$: 將$n$個整數表示成\textbf{n進位}數，每個數由$2$-digit表示，範圍$0$到$n - 1$，再用radix sort對$2$-digit排序，共兩次。
        \item If max frequency is $\le 2$ times of min frequency, Huffman code is \textbf{NOT} always better than an ordinary fixed-length code.
        \item Amortized analysis與average-case analysis無關。
        \item (\textbf{FALSE}) \textbf{If} a graph has a unique MST then, for every cut of the graph, there is a \textbf{unique light edge} crossing the cut.
        \item (\textbf{TRUE}) A graph has a unique MST \textbf{if}, for every cut of the graph, there is a \textbf{unique light edge} crossing the cut.
        \item The worst-case running time and expected running time are equal to within \textbf{constant} factors for any randomized algorithm.
        \item Selection problem: $T(n) = T(\frac{n}{5}) + T(\frac{3n}{4}) + O(n)$
        \item Given an \textbf{undirected} graph and a positive integer $k$, is there a path of length $\le k$, which each edge has weight $1$ and each vertex is visited \textbf{exactly} once: P, solved by Floyd-Warshall algorithm.
        \item Given an \textbf{undirected} graph and a positive integer $k$, is there a path of length $\ge k$, which each edge has weight $1$ and each vertex is visited $\le$ once: NPC.
        \item A flow network of multiple sources can be reduced to a single source.
        \item Subset sum: $s(i, j)$: sum $j$ can be found in $\{a_1, \ \cdots, a_i\}$ \begin{equation}
            s(i, j) = \begin{cases}
                0 &, i = 0 \\
                1 &, j = 0 \\
                s(i - 1, j) \lor s(i - 1, j - v_i) &, j \ge v_i
            \end{cases}
        \end{equation} result is $s(m, n)$.
        \item Hanoi tower iterative version: Check if the \textbf{input number} $n$ is even or odd. \\ 
        If $n$ is even, \begin{equation}
            \begin{cases}
                A \leftrightarrow C \\
                A \leftrightarrow B \\
                C \leftrightarrow B
            \end{cases} 
        \end{equation} If $n$ is odd, \begin{equation}
            \begin{cases}
                A \leftrightarrow B \\
                A \leftrightarrow C \\
                B \leftrightarrow C
            \end{cases} 
        \end{equation}
        \item Fibonacci search: \begin{lstlisting}[caption={Fibonacci search.}, captionpos=b, language=Python]
            def fibSearch(arr, data):
                max = len(arr) - 1
                y = getY(fib, max + 1) # Find the largest index, which its value is smaller than data.
                m = max - fib[y] 
                x = y - 1
                i = x
                if arr[i] < data: # Check at first.
                    i += m
                while fib[x] > 0:
                    if arr[i] < data:
                        x -= 1
                        i += fib[x]
                    elif arr[i] > data:
                        x -= 1
                        i -= fib[x]
                    else:
                        return i
                return -1
        \end{lstlisting}
        \item Box stacking: \begin{enumerate}
            \item Generate all $3$ rotations of all boxes. We consider width as always smaller than or equal to depth.
            \item Sort the above generated $3n$ boxes in \textbf{decreasing} order of \textbf{base area}.
            \item $msh(i)$: Max possible stack height with box $i$ at top of stack. \begin{equation}
                \begin{aligned}
                    msh(i) = \{& \max \{msh(j)\} + height(i)\}, \\ 
                    & \forall j < i \land width(j) > width(i) \land depth(j) > depth(i)
                \end{aligned}
            \end{equation} result is \begin{equation}
                \max_{0 < i < n}\{msh(i)\}
            \end{equation}
        \end{enumerate}
        \item Building bridge: \begin{enumerate}
            \item Sort the north-south pairs on the basis of \textbf{increasing} order of \textbf{south} x-coordinates.
            \item Find \textbf{LIS} of north x-coordinates.
        \end{enumerate}
        \item Optimal strategy: $f(i, j)$: max value the user can collect from $i$-th coin to $j$-th coin.\begin{equation}
            f(i, j) = \begin{cases}
                v_i &, j = i \\
                \max\{v_i, v_j\} &, j = i + 1 \\
                \begin{aligned}
                    \max\{& v_i + \min\{f(i + 2, j), f(i + 1, j -1)\}, \\
                    & v_j + \min\{f(i + 1, j -1), f(i, j - 2)\}\}
                \end{aligned} &, \text{otherwise}
            \end{cases}
        \end{equation}
        \item (TIOJ-1097) Find the largest square submatrix with all 0s in a 0/1 matrix: $dp(i, j)$: max square submatrix in $i \times j$ left upper submatrix. \begin{equation}
            dp(i, j) = \min\{dp(i − 1, j − 1), dp(i, j − 1), dp(i − 1,j)\} + 1
        \end{equation} 
        \item (UVA-10934) Dropping water balloons ($k$ balloons and height $n$): $dp(i, j)$: max height $i$ balloons can be dropped $j$ times. \begin{equation}
            dp(i, j) = \begin{cases}
                dp(i, j - 1) + dp(i - 1, j - 1) + 1 &, arr(i, j) = 1 \\
                0 &, arr(i, j) = 0
            \end{cases}
        \end{equation} result is \begin{equation}
            \min_{j} \{dp(k, j) \ge n\}
        \end{equation}
        \item (TIOJ-1471) Skyline: $dp(i, j)$: walk $i$ distance and height is $j$. \begin{equation}
            \begin{cases}
                dp(i, j) & = dp(i - 1, j - 1) + sum(j) \\
                sum(j) & = sum(j) -dp(i - j, j) + dp(i, j)
            \end{cases}
        \end{equation} result is \begin{equation}
            \sum_{j}dp(n, j)
        \end{equation}
        \item Largest rectangle in histogram: \begin{itemize}
            \item If the new element is higher than stack top element, push it; otherwise, pop and calculate the area until the new element is higher than stack top element.
            \item Maximal rectangle: Similarly, for each column, the count of $1$ of each row, can be seen as the element.
        \end{itemize}
    \end{itemize}
\end{theorem}
