\item \begin{theorem}{(34)} Virtual machine：\begin{itemize}
        \item Host：Underlying hardware system.
        \item Virtual Machine Manager (VMM, Hypervisor).
        \item Guest：Process provided by VM, for example, OS, applications.
        \item Implementations：\begin{itemize}
            \item Type 0：Hardware.
            \item Type 1：Kernel mode. \begin{itemize}
                \item OS-like software：只提供virtualization。
                \item General-purpose OS在kernel mode提供VMM services。
            \end{itemize}
            \item Type 2：User mode：Applications that provide VMM services.
        \end{itemize}
        \item Virtualization variations：\begin{itemize}
            \item Paravirtualization：Present guest similar but NOT identical to host hardware. Guest should be modified to run on paravirtualized hardware.
            \item Emulators：Applications to run on a different hardware environment.
            \item Application containment (container)：Not virtualization at all, but provides segregating applications from the OS.
        \end{itemize}
        \item Java Virtual Machine (JVM)：只提供規格（class loader，class verifier和Java interpreter），並非實現。
        \item 優點：\begin{itemize}
            \item 提供Cloud computing。
            \item 測試中的OS掛了，視為一個user process掛掉，其他user processes以及real system不受影響。
        \end{itemize}
        \item 缺點：\begin{itemize}
            \item 不易開發VMM，因為要複製與底層host hardware一模一樣的VM非常困難，例如modes control and transition、資源調度和I/O device and controller之模擬。
            \item 效能比host hardware差。
        \end{itemize}
    \end{itemize}
\end{theorem}

\item \begin{theorem}{(52)} \quad\quad \begin{itemize}
        \item Software as a service（SaaS）：Applications, e.g. Dropbox, Gmail.
        \item Platform as a service（PaaS）：Software stack, i.e. APIs for softwares, e.g. DB server.
        \item Infrastructure as a service（IaaS）：Servers or storage, e.g. storage for backup.
    \end{itemize}
\end{theorem}

