\item \begin{theorem}{(203)} \begin{equation}
        \text{Rotational time} = \frac{0.5}{\text{RPS}}
    \end{equation} 
\end{theorem}

\item \begin{theorem}{(207)} Flash：\begin{itemize}
        \item NOT lost info if it loses power.
        \item Write is much slower than read.
        \item NOR flash：Read access time computation is similar to DRAM. 
        \item NAND flash：Read bandwidth computation is similar to disk. Much cheaper per GB.
    \end{itemize}
\end{theorem}

\item \begin{theorem}{(210, 213, 278, 289)} RAID：\begin{itemize}
        \item Dependability：服務品質。
        \item Reliabilitiy：時間區間內可以正確執行其功能的機率。
        \item Availability：某時間點可以正確執行其功能的機率。\begin{equation}
            \text{Availability} = \frac{\text{MTTF}}{\text{MTTF} + \text{MTTR}}
        \end{equation}
        \item Data stripping：Data分散到不同disks，一次data存取會使多個disks存取，提升performance，但不能改善reliability。
        \item Redundancy：利用多餘disks提升availablity，但不能改善reliability。
        \item RAID 0：Block-stripping，非容錯，沒有多餘disks。
        \item RAID 1：Mirroring (shadowing)，最貴，data總是有額外一個copy，$2n$ disks。
        \item RAID 2：Hamming code，Write需要讀取所有disks，從新計算Hamming code並寫入ECC disks，效率差，$2n - 1$ disks。
        \item RAID 3：\begin{itemize}
            \item Bit-interleaved parity.
            \item Reliability和RAID 2相同。
            \item 不做備份，花費較多時間恢復data，$n + 1$ disks。
            \item 當$1$個disk出錯可救回來，多個則否。
            \item Availability cost為$\frac{1}{N}$，其中$N$為protection group disks數量。
            \item Parity集中存放一個disk。
        \end{itemize}
        \item RAID 4：\begin{itemize}
            \item Block-interleaved parity。
            \item 只對protection group其中一disk做small reads。
            \item $n + 1$ disks，parity集中存放一個disk。
            \item 當$1$個disk出錯可救回來，多個則否。
        \end{itemize}
        \item RAID 5：\begin{itemize}
            \item Distributed Block-interleaved parity
            \item Write就不會有單一disk瓶頸
            \item $n + 1$ disks，parity被分散到所有disks。
        \end{itemize}
        \item RAID 0與RAID 1組合：\begin{itemize}
            \item RAID 0+1：先stripping，再整體mirror。一個disk壞，需整組copy替換。
            \item RAID 1+0：先個別mirror，再交錯stripping。一個disk壞，只需該disk的copy替換，較好。
        \end{itemize}
        \item Read latency：RAID 3最短；Write latency：RAID 0 或 RAID 3最短。
        \item RAID 3 has worst throughput for small writes.
        \item RAID 3, 4, 5 have same throughput for large writes.
        \item RAID 4, 5 perform same for parallel small reads and small writes, but RAID 3 can NOT for both access.
    \end{itemize}
\end{theorem}